---
title: "Practical Machine Learning"
author: "Jonathan Pavkov"
date: "Tuesday, December 22, 2015"
output: html_document
---

### Overview
To start the analysis, I removed variables that had a near zero variance using the nearZeroVar function. Following this I removed the name and identifier columns, as well as date (figuring the date shouldn't have an impact on predicting the exercise type). Finally, I removed all columns that had NA.
```{r, warning=FALSE}
options(width = 10000)
setwd("C:/devl/Coursera/08 Practical Machine Learning/project")  
library(rattle)
library(caret)
training <- read.csv("pml-training.csv")
testing <- read.csv("pml-testing.csv")
nsv <- nearZeroVar(training,saveMetrics=FALSE)
training <- training[,-nsv]
training <- training[,c(-2,-5)]
training <- training[,-1]
training <- training[,colSums(is.na(training)) == 0]
```

### Model Used
I used the random forest method for the training set. This was because it was the only type of training that I could do in under 10+ minutes of processing time.

```{r, eval=FALSE}
mtryGrid <- expand.grid(mtry = 100)
training_subset <- training[sample(1:nrow(training), 1000, replace=FALSE),]
modFit_rf <- train(classe ~ .,data=training_subset,method="rf",tuneGrid=mtryGrid)
modFit_rf
```

```{r, echo=FALSE}
load(file="modFit_rf")
load(file="pred_rf")
```

```{r, echo=FALSE}
modFit_rf
```

The resampling Accuracy is 91.4%, and the resampling Kappa is 89.1%
1. Cross Validation: bootstrapped, 25 times
2. Expected out of sample error: 10%, based on 2 / 20 of the test set provided not being accurate.

### Outcome
In the predictions below, 18 of them were accurate.
```{r}
pred_rf <- predict(modFit_rf,testing)
pred_rf
```

### Conclusions
The random forest model was a good choice, and was accurate 90% of the time on the test data set. With more processing power, it would be nice to explore other modeling techniques and compare results.
